Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2011-11-14 Multiresolution_framework/ltx/manuscript.tex
changed RMSE plot to MRMSE

To study the performance of different models with various MRA capabilities, a single realisation was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment. The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$. The RMSE of the field estimation at different levels of approximation is shown in Figure~\ref{fig:RMSE}. By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.78, confirming that $j=3$ is in fact adequate to capture the dynamics of the underlying field. The estimated field at a single time instant is shown in Figure~\ref{fig:FieldEstimates200}. The experiment was performed several times and the results were consistent over each run.

@@

 		\caption{{\bf Error in the field reconstruction for experiment II}. RMSE of the estimated field of models with different level of approximations. $j=0$, $RMSE = 1.93$; $j=1$, $RMSE = 1.39$; $j=2$, $RMSE = 0.90$; $j=3$, $RMSE = 0.78$; $j=4$, $RMSE=0.78$}

>>>>

To study the performance of different models with various MRA capabilities, a single realisation was obtained using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation} under the same circumstances of the previous experiment. The generated data set was then employed to estimate the underlying field and the connectivity kernel parameters using different state-space models, $j=0$ up to $j=4$. The RMSE of the field estimation at different levels of approximation is shown in Figure~\ref{fig:RMSE}. By increasing the value of $j$, error in the estimation decreases and converges to a steady value of 0.71, confirming that $j=3$ is in fact adequate to capture the dynamics of the underlying field. The estimated field at a single time instant is shown in Figure~\ref{fig:FieldEstimates200}. The experiment was performed several times and the results were consistent over each run.

@@

 		\caption{{\bf Error in the field reconstruction for experiment II}. MRMSE of the estimated field of models with different level of approximations. $j=0$, $RMSE = 1.83$; $j=1$, $RMSE = 1.41$; $j=2$, $RMSE = 0.83$; $j=3$, $RMSE = 0.71$; $j=4$, $RMSE=0.71$}
